Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-13 thesis_main.tex
s

\documentclass[letterpaper,12pt,draft]{yalephd}
% remove draft option for final printing.
% font size must be between 10pt-12pt.

\usepackage{geometry} % you need this for yalephd.cls to work.
\usepackage{graphicx} % you probably want the rest of these.
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{comment}
\usepackage{cite}
\bibliographystyle{plain}

@@

@@

%  \begin{dedication}
%A mia mamma e mio babbo,\\
%grazie per le radici e grazie per le ali.
%    \par   %% or a blank line
%    \vspace{2\baselineskip}
%To my mom and dad,\\
%thank you for the roots and thank you for the wings.
%    \vspace{\baselineskip}
%  \end{dedication}
\tableofcontents
\listoffigures % remove this if you have no figures.
\listoftables % remove this if you have no tables.

\chapter{Acknowledgements} % this needs to be before \mainmatter.
A lot of people are awesome. But not you, who are reading my thesis before it's done.

% Starts proper arabic numbering of pages and chapters.
\mainmatter

\input{0-Introduction}
\input{1-LArTPCs}
\input{2-TheLArIATExperiment}
\input{3-KaonInteractionsInLAr}
\input{4-DataCollection}
\input{5-EnergyCalibration}
\input{6-TrackingOptimization}
\input{7-KaonCrossSectionAnalysis}

>>>>

\documentclass[letterpaper,12pt]{yalephd}
% remove draft option for final printing.
% font size must be between 10pt-12pt.
\usepackage{caption,setspace}
\usepackage{amsmath} 
\usepackage{rotating}

\usepackage{geometry} % you need this for yalephd.cls to work.
\usepackage{graphicx}
\usepackage[graphicx]{realboxes}
 % you probably want the rest of these.
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{hyperref}

\usepackage{mathtools}
\DeclarePairedDelimiter\bra{\langle}{\rvert}
\DeclarePairedDelimiter\ket{\lvert}{\rangle}
\DeclarePairedDelimiterX\braket[2]{\langle}{\rangle}{#1 \delimsize\vert #2}
\usepackage{textgreek}

\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{comment}
\usepackage{cite}
\usepackage{color}
\bibliographystyle{plain}
\usepackage{slashed}

\setcounter{chapter}{-1}

@@

\usepackage{lineno,xcolor}

\linenumbers

@@

  \begin{dedication}
A mia mamma e mio babbo,\\
grazie per le radici e grazie per le ali.
    \par   %% or a blank line
    \vspace{2\baselineskip}
To my mom and dad,\\
thank you for the roots and thank you for the wings.
    \vspace{\baselineskip}
  \end{dedication}

\tableofcontents
%\listoffigures % remove this if you have no figures.
%\listoftables % remove this if you have no tables.

\chapter{Acknowledgements} % this needs to be before \mainmatter.

{\raggedleft ``\emph{Dunque io ringrazio tutti quanti.} \par}
{\raggedleft \emph{Specie la mia mamma che mi ha fatto cos\'i funky.}"\par}
{\raggedleft -- Articolo 31, Tanqi Funky, 1996 -- \par}
\vspace{0.5cm}

{\raggedleft ``\emph{At last, I thank everyone.} \par}
{\raggedleft \emph{Especially my mom who made me so funky.}"\par}
{\raggedleft -- Articolo 31, Tanqi Funky, 1996 -- \par}
\vspace{0.5cm}

A lot of people are awesome, especially you, since you probably agreed to read this when it was a draft.

%Bonnie. I don't even know where to start.
%Flavio
%

%A big thank you to my academic sisters, a bunch of extraordinary women who have taught me so much about myself and our field.
%From the youngest to the oldest (again academically speaking): Supraja, you worked the magic of enriching my past, thank you from the bottom of my heart;  Brooke, the depth of your knowledge, your drive and love for our field has been and will always be a constant inspiration;  Ariana, thanks for keeping me sane for the last four years, if you run for president, remember to delete  our Skype chats, love and hugs to you dudette; and last but not least Xiao, I don't think Fermilab has given me a bigger gift than your friendship.

%Shany
%Jen 
%Jonathan
%Andrzej
%Anto
%LArIAT & MicroBooNE
%Louise

% Starts proper arabic numbering of pages and chapters.
\mainmatter
%\input{Chapters/0-Introduction}
%\input{Chapter-1/1-Theory}
%\input{Chapter-2/2-LArTPCs}
%\input{Chapter-3/3-TheLArIATExperiment}
\input{Chapter-4/4-Methodology}

\input{Chapter-5/5-Preparatory}
\input{Chapter-6/6-PionCrossSection}
\input{Chapter-7/7-KaonCrossSection}

%\input{Chapter-7/7-BackgroundSub}
%\input{Chapter-8/8-CrossSectionAnalysis}\input{Chapter-9/9-Uncertainty}

% Only call appendix once, here.
\appendix
%\input{Chapters/A-KaonAna}
\input{AppendixB-EField/B-LArIATEField}
%\input{Chapters/C-MicroBooNECRT}

% Old chapters configuration %
%\input{Chapters/4-DataCollection}
%\input{Chapters/4-MonteCarlo}
%\input{Chapters/5-EnergyCalibration}
%\input{Chapter-8/8-TrackingOptimization}
